---
title: "International VAIAK"
format: 
  html: 
    toc: true            # Table of content (Menu)
    toc-depth: 3         # Level of headings 
    toc-location: left   # Position 
    toc-title: "Contents" # Name
    page-layout: article
execute:
  echo: FALSE    
  warning: FALSE
  message: FALSE
  output: TRUE
---

```{r}
library(dplyr)
library(tidyr)
library(ggiraph) # interactive plot
library(htmlwidgets) # interaction online
library(ggplot2)
library(sf) # world map
library(patchwork)
```

# Introduction

```{r, results='hide', fig.show='hide'}

data = read.csv("International_vaiak.csv")

```

A total of 68 datasets were collected. The number of participants, languages, etc. depend on which scale we are analysing. Thus, the presentation will be divided into three parts:

-   Art Interest, where only the participants that have answered to all the AI items are selected

-   Art Knowleedge, where only the participants that have answered to all the Part B items (given that it is expected to have empty Part C items) are selected

-   Full scale, where participants that completed correctly the both scales are presented

This first presentation is just to understand the number of participants for each of the different variables

# Art Interest

This is the number of participants divided for the datasets. 

```{r, results='hide', fig.show='hide'}

data_ai = data %>%
    filter(
      if_all(AI_1_1:AI_2_4, ~ !is.na(.x))) %>%
  mutate(
    ID_Database = factor(ID_Database))

```

```{r}

data_ai_participant = data_ai %>%
count(ID_Database, name = "n")

graph_ai = ggplot(data_ai_participant, aes(y = n, x = reorder(ID_Database, n),
                                tooltip = paste0(ID_Database, ": ", n), 
                                data_id = ID_Database)) +
  geom_col_interactive(fill = "grey70",
                        hover_css = "fill:#4A90E2; 
                       stroke:#2C5D87; 
                       stroke-width:1.5px;") +
  coord_flip() + 
  theme_minimal() +
  labs(title = "Variable : Art Interrest")  +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.position = "none")

girafe(ggobj = graph_ai) 

```

This is the number of participants for settings

```{r}

data_ai_context = data_ai %>%
  count(Sett_Context, name = "n")

graph_ai = ggplot(data_ai_context, aes(y = n, x = reorder(Sett_Context, n),
                                tooltip = paste0(Sett_Context, ": ", n), 
                                data_id = Sett_Context)) +
  geom_col_interactive(fill = "grey70",
                        hover_css = "fill:#4A90E2; 
                       stroke:#2C5D87; 
                       stroke-width:1.5px;") +
  theme_minimal() +
  labs(title = "Variable : Context in AI scale")  +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.position = "none")

girafe(ggobj = graph_ai) 
```

# Art Knowledge

This is the number of participants divided for the datasets. 

```{r, results='hide', fig.show='hide'}

data_ak = data %>%
    filter(
      if_all(B1:B6, ~ !is.na(.x)) |
        if_all(B1_Numeric:B6_Numeric, ~ !is.na(.x))) %>%
  mutate(
    ID_Database = factor(ID_Database))

```

```{r}

data_ak_participant = data_ak %>%
  count(ID_Database, name = "n")

graph_ak = ggplot(data_ak_participant, aes(y = n, x = reorder(ID_Database, n),
                                tooltip = paste0(ID_Database, ": ", n), 
                                data_id = ID_Database)) +
  geom_col_interactive(fill = "grey70",
                        hover_css = "fill:#4A90E2; 
                       stroke:#2C5D87; 
                       stroke-width:1.5px;") +
  coord_flip() + 
  theme_minimal() +
  labs(title = "Variable : Art Knowledge")  +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.position = "none")

girafe(ggobj = graph_ak) 

```


```{r}

world_sf = read_sf("https://raw.githubusercontent.com/holtzy/R-graph-gallery/master/DATA/world.geojson")

data_ak_country = data_ak %>%
  count(Dem_Country, name = "n") %>%
  filter(n>5)

world_sf = world_sf %>%
    filter(!name %in% c("Antarctica", "Greenland"))  %>%
  left_join(data_ak_country, by = c("name" = "Dem_Country")) 

graph_ak_country_1 = ggplot(world_sf, aes(
  x = reorder(name, n),
  y = n,
  tooltip = name,
  data_id = name,
  fill = name)) +
  geom_col_interactive(data = filter(world_sf, !is.na(n))) +
  theme_minimal() +
    coord_flip() + 
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.position = "none")

graph_ak_country_2 = ggplot() +
  geom_sf(data = world_sf, fill = "lightgrey", color = "lightgrey") +
  geom_sf_interactive(
    data = filter(world_sf, !is.na(n)),
    aes(fill = name,
      tooltip = paste0(name, ":", n),
      data_id = name)) +
  coord_sf(crs = st_crs(3857)) +
  theme_void() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.position = "none")

combined_ak_country = graph_ak_country_1 / graph_ak_country_2 + plot_layout(heights = c(2,2))

interactive_plot = girafe(ggobj = combined_ak_country, 
                            width_svg = 10, height_svg = 14)

interactive_plot = girafe_options(
  interactive_plot,
  opts_hover(css = "fill:red;stroke:black;"))

interactive_plot
```



